\centerline{\textbf{Project Summary}}
In the contemporary healthcare landscape, the demand for quick and accurate medical diagnostics is more critical than ever, especially in the wake of global health crises. Medibot, an advanced Medical Diagnosis AI Assistant, leverages Computer Vision (CV) and Natural Language Processing (NLP) to enhance the efficiency and accessibility of medical consultations. The platform addresses key challenges in medical diagnostics by providing robust analysis of medical images and symptom-based consultations.

Medibot features an integrated suite of tools that include:
\begin{itemize}
    \item Advanced neural networks for detailed analysis of chest X-rays, capable of identifying a wide range of conditions.
    \item Optical Character Recognition (OCR) to convert images of blood lab reports into text, followed by deep NLP to provide simplified and accurate interpretations.
    \item Llama models that manage symptom extraction, facilitate user interactions, and ensure accurate routing between various AI agents for comprehensive diagnostic support.
\end{itemize}

Accessible via a user-friendly web interface and a mobile application, Medibot is designed to streamline the initial stages of medical diagnostics, guiding patients quickly to appropriate medical advice and care. The system's architecture utilizes modern technologies such as Docker, Node.js, MongoDB, and Milvus to ensure reliability and scalability.

Medibot stands out by providing a highly interactive, intuitive, and efficient AI-driven diagnostic process, significantly enhancing patient engagement and outcomes in healthcare.

\begin{abstract}
Medibot revolutionizes medical diagnostics by integrating sophisticated Computer Vision and Natural Language Processing technologies to provide rapid, accurate, and accessible healthcare diagnostics. This AI-driven platform facilitates detailed medical image analysis and interactive symptom-based consultations, enabling efficient preliminary diagnostics and specialist referrals. With its comprehensive suite of diagnostic tools, including image classification, text extraction, and AI-based symptom analysis, Medibot enhances the diagnostic process, reduces the dependency on extensive medical consultations, and improves healthcare accessibility. Deployed via an intuitive web and mobile interface and built with cutting-edge technology, Medibot offers a transformative solution for early medical diagnosis, contributing significantly to improved healthcare outcomes.
\end{abstract}
